Supplemental material for `Eliminating object prior-bias from sparse-projection tomographic reconstructions'

### 2021-10-15 paper/changes.tex
Final set of changes

    \textit{That said, the goal of our previous and curent work is to provide
    a technique that can improve upon a chosen baseline reconstruction
    when measurements are extremely sparse.  One may choose any
    baseline reconstruction (including an inferior -- for this dataset
    -- Compressed sensing prior) for pedagogical, historical, or
    commercial reasons, and given that, our key question is -- is
    there a way to improve?  The spatially-varying method of
    moderating the prior settles this question.}

@@

   We accept this point, and have now discussed the difficulties in
   using deep-learning techniques for the current problem in Section.~7C
   of our paper.

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. In order to use the Discrete Algebraic Reconstruction Technique (DART)~\cite{dart}, one must assume the imaged object to be made of only a few fixed number of known attenuation coefficients. Since we do not make any such assumption about  our datasets, we have not used DART. %% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~7 (Section-6A) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

We accept this point, and present details in Section.~7B of our paper.
We also provide the code to reproduce the compute time claimed.

>>>>

    \textit{That said, the goal of our previous and current work is to provide
    a technique that can improve upon a chosen baseline reconstruction
    when measurements are extremely sparse.  One may choose any
    baseline reconstruction (including an inferior -- for this dataset
    -- Compressed sensing prior) for pedagogical, historical, or
    commercial reasons, and given that, our key question is -- is
    there a way to improve?  The spatially-varying method of
    moderating the prior settles this question.}

@@

   We accept this point, and have now discussed the difficulties in
   using deep-learning techniques for the current problem in Section.~7B
   of our paper.

@@

 Among the family of algebraic techniques, we have compared our method
 with Algebraic Reconstruction Technique (ART)~\cite{art} and Simultaneous
 Algebraic Reconstruction Technique (SART)~\cite{sart}. In order to use the Discrete Algebraic Reconstruction Technique (DART)~\cite{dart}, one must assume the imaged object to be made of only a few fixed number of known attenuation coefficients. Since we do not make any such assumption about  our datasets, we have not used DART. %% IS THERE A NEED TO HIGHGLIHT what we have not done?  Also give references?
 Among other iterative techniques, we
 have used Simultaneous Iterative Reconstruction Technique (SIRT)~\cite{sirt},
 Total Variation (TV)~\cite{TV},~\cite{TVReg} and Compressed Sensing (CS)~\cite{lasso} with Haar wavelet
 and DCT as sparsity basis. The details of solvers used for these
 algorithms and their reconstructions are in Page.~8 (Section 6B) of
 the paper. For CS reconstruction, we observed that Haar wavelet and
 DCT were best suited for our dataset among various other possible
 sparsity basis.

@@

We accept this point, and present details in Section.~7A of our paper.
We also provide the code to reproduce the compute time claimed.

### 2021-10-15 paper/post_tci.tex
Final set of changes

reconstruction (also see Sec~3 of \cite{supp_paper}.

@@

        these reconstructions is shown in

@@

\subsubsection{Example Computation}
If the set of projection views for every test is fixed a priori, a
reasonable assumption, the set of low quality reconstructions can be
produced offline and stored in order to save computational costs. 
% Most of the computation time in our technique is used for the
% generation of low quality eigen-space by reconstructing each of the
% templates using TV and FDK. 
With this as the basis, Table~\ref{table:compute_time} shows the
computation times for various stages of reconstruction of a 2D slice
of Liver on MATLAB 2019a on an AMD
2920X 12-Core Processor machine with 64GB RAM. 
% If however, new sets of
% projection views for every test are to be allowed, the low quality
% reconstructions can still be performed efficiently using
% parallelization since these reconstructions are completely
% independent. 
\begin{table}[!h]
 \centering
  \caption{Computation times (in seconds) for various stages of
    reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD
    2920X 12-Core Processor machine with 64GB RAM. Our code is
    available for inspection~\cite{codeRepo}.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parameteric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learned by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

@@

%--------------------------Conclusion-----------------------
\section{Conclusions}
\label{sec:conclusions}
This work deals with the effective use of priors for tomographic
reconstruction in longitudinal studies. When the number of measurements 
impedes the benefit of applying classic regularization methods, we discuss the utility of
using information from previous scans of the same object, as outlined in
Figs.~\ref{fig:story} and~\ref{fig:prior_overview}. In order to observe details of new changes
accurately, we use a novel
spatially-varying prior-based method. This method ensures that the
reconstruction of localized new information in the data is not
affected by the priors, while the other relatively stationary regions benefit from the extra prior information. %Based on the potato and the okra experiments,
%we see that our method is able to \emph{discover both} the presence of
%a new structure, as well as the absence of a structure.
We have thus
improved state of the art by detecting the strength and location
of these regions of change and
assigning low prior weights wherever necessary. This innovation becomes evident through the weights maps shown here in Figures~\ref{fig:weights_map_2Dpotato} and~\ref{fig:few_view_okra_2D_weights}. The probability of
presence of a `new region' is enhanced considerably by a novel
combination of different reconstruction techniques.  We have validated
our technique on medical 2D and real, biological 3D datasets for
longitudinal studies. The method is also largely robust to the number
of previously scanned objects used. We urge the reader to see the
videos of reconstructed volumes in the supplementary
material~\cite{supp_paper}.
%Our method has been shown to make the best use of prior
%only when needed, thus detecting new changes of the test
%data.

>>>>

reconstruction (also see Sec~3 of \cite{supp_paper}).

@@

        these reconstructions are shown in

@@

\subsubsection{Example Computation}
If the set of projection views for every test is fixed a priori, a
reasonable assumption, the set of low quality reconstructions can be
produced offline and stored in order to save computational costs. 
% Most of the computation time in our technique is used for the
% generation of low quality eigen-space by reconstructing each of the
% templates using TV and FDK. 
With this as the basis, Table~\ref{table:compute_time} shows the
computation times for various stages of reconstruction of a 2D slice
of Liver on MATLAB 2019a on an AMD
2920X 12-Core Processor machine with 64GB RAM. 
% If however, new sets of
% projection views for every test are to be allowed, the low quality
% reconstructions can still be performed efficiently using
% parallelization since these reconstructions are completely
% independent. 
\begin{table}[!h]
 \centering
  \caption{Computation times (in seconds) for various stages of
    reconstruction of a 2D slice of Liver on MATLAB 2019a on an  AMD
    2920X 12-Core Processor machine with 64GB RAM. Our code is
    available for inspection~\cite{codeRepo}.}
\begin{tabular}{|l|l|l|l|}
\hline
 \begin{tabular}[c]{@{}l@{}} FBP (Sufficient \\ views)\end{tabular}             & \begin{tabular}[c]{@{}l@{}} TV (Moderate \\ views)  \end{tabular}                      & \begin{tabular}[c]{@{}l@{}}Computation of \\ weights map \\ (Very few \\views)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Alternate\\ Minimization \\ (Very few \\views)\end{tabular} \\ \hline
\multicolumn{1}{|c|}{0.01} & \multicolumn{1}{c|}{5.63} & \multicolumn{1}{c|}{0.01}                                             & \multicolumn{1}{c|}{34.00}                                                                     \\ \hline
\end{tabular}
\label{table:compute_time}
\end{table}
\subsection{Requirements for applying deep learning techniques}
Deep learning techniques are powerful tools to learn an unknown
parametric function relating an input space and an output space. In such
settings, our current goal of detecting new changes is a `prediction'
problem in a continuous solution space i.e., \textit{``given
  intensities of a voxel at various time instants in a longitudinal
  setting and partial measurements of the voxel at the current time,
  what will be the intensity of the same voxel at the current time
  instant?''}. This estimation can be learned by a deep neural network
if there are hundreds of labeled data.  However, generalization of
this across multiple datasets poses a question mark.

@@

%--------------------------Conclusion-----------------------
\section{Conclusions}
\label{sec:conclusions}
This work deals with the effective use of priors for tomographic
reconstruction in longitudinal studies. When the number of measurements 
impedes the benefit of applying classic regularization methods, we discuss the utility of
using information from previous scans of the same object, as outlined in
Figs.~\ref{fig:story} and~\ref{fig:prior_overview}. In order to observe details of new changes
accurately, we use a novel
spatially-varying prior-based method. This method ensures that the
reconstruction of localized new information in the data is not
affected by the priors, while the other relatively stationary regions benefit from the extra prior information. %Based on the potato and the okra experiments,
%we see that our method is able to \emph{discover both} the presence of
%a new structure, as well as the absence of a structure.
We have thus
improved state of the art by detecting the strength and location
of these regions of change and
assigning low prior weights wherever necessary. This innovation becomes evident through the weights maps shown in Figure~\ref{fig:weights_map_2Dpotato} and the resulting reconstructions shown in Figure~\ref{fig:reconstructions_diff_methods}. The probability of
presence of a `new region' is enhanced considerably by a novel
combination of different reconstruction techniques.  We have validated
our technique on medical 2D and real, biological 3D datasets for
longitudinal studies. The method is also largely robust to the number
of previously scanned objects used. We urge the reader to see the
videos of reconstructed volumes in the supplementary
material~\cite{supp_paper}.
%Our method has been shown to make the best use of prior
%only when needed, thus detecting new changes of the test
%data.

### 2021-10-15 paper/post_tci_supplementary.tex
saving suppl edits
Final set of changes

  \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
\end{itemize}

@@

The value of $k$ (discussed in Sec.~7 of the main paper) is typically
dependent on the number of false positives the system can allow in
exchange for the detection of more true positives (regions of new
changes). It is this choice and not the particular type of dataset
that affects the selection of $k$. In our work, the chosen $k$
corresponds to the one that gives minimal tolerance to false
positives. However, in case one wishes to completely avoid the use of
this hyper-parameter, one can construct a binary weights-map using a
method described below.

@@

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$), the prior and the pilot
can be stitched in a simplistic way using the equation 
$\boldsymbol{W_b}(\rm{Pilot}) + (1-\boldsymbol{W_b})(\rm{Prior})$.
The advantage of this method is that the computational time is
signficantly reduced since the alternate minimization procedure is not
used.

@@

\begin{figure}[]
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
        \caption{}
     \end{subfigure}
     \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}

        \caption{}
    \end{subfigure}    
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
        \caption{}
     \end{subfigure}
     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map. (a)-(c) the images used as object-prior, (d) the test (310$\times$310). Measurements along $60$ views were taken. (e) error-map showing new regions, (f) detected binary weights map showing regions of new changes, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions. } %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates, 
\label{fig:okra_svm}
\end{figure}
%\clearpage
%\newpage

@@

>>>>

    \url{https://www.dropbox.com/sh/y6s4h2p04tp1lgq/AADn2q43o7SYj10rmheMCDzZa?dl=0}
 \item \textbf{Okra:}

  \url{https://www.dropbox.com/sh/vkol8aluzsnusfo/AABtu6-M1LKOsQjKIjxlSxUfa?dl=0}
\end{itemize}

@@

The value of $k$ (discussed in Sec.~6A of the main paper) is typically
dependent on the number of false positives the system can allow in
exchange for the detection of more true positives (regions of new
changes). It is this choice and not the particular type of dataset
that affects the selection of $k$. In our work, the chosen $k$
corresponds to the one that gives minimal tolerance to false
positives. However, in case one wishes to completely avoid the use of
this hyper-parameter, one can construct a binary weights-map using a
method described below.

@@

We mention in passing that if we are to entirely avoid the other
parameters (viz. $\lambda_1$ and $\lambda_2$), the object-prior and the pilot
can be stitched in a simplistic way using the equation

$\boldsymbol{W_b}*(\rm{pilot}) + (1-\boldsymbol{W_b})*(\rm{object\textrm{ }prior})$.
The advantage of this method is that the computational time is
significantly reduced since the alternate minimization procedure is not
used.

@@

\begin{figure}[]
    \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_1.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_2.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/template_3.png}
        \caption{}
     \end{subfigure}
     \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/testIm.png}
        \caption{}
     \end{subfigure}
    \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/weights.png}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/detectedInlier.png}
        \caption{}
    \end{subfigure}
     \caption[Selecting $k$]{Using an alternate approach to generate (binary) weights map. (a)-(c) the images used as object-prior, (d) the test (310$\times$310). Measurements along $60$ views were taken. (e) error-map showing new regions, (f) detected binary weights map showing regions of new changes.}%, (g) pilot, (h) final reconstruction with pilot in the new regions, and prior in the other regions. } %(h) prior, which is obtained by projecting the pilot onto the eigenspace computed from the templates, 
\label{fig:okra_svm}
\end{figure}
%\clearpage
%\newpage

@@

    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/result_pilot.png}

        \caption{}
    \end{subfigure}    
    \begin{subfigure}[b]{0.24\linewidth}
        \includegraphics[width=\textwidth]{../images/svm/okra/resultStitched_svm.png}
        \caption{}
     \end{subfigure}
